Toxic Code Snippets on Stack Overflow

### 2018-11-15 cloverflow-tse/cloverflow.tex
Finalised the response letter. Ready for Jens to look at.

Toxic code snippets mean code snippets that, after incorporating into software,
the cost of paying back the technical debt exceeds the value it generates in the long run.
Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1)~outdated, (2)~violating their original software
license, (3) exhibiting code smells, or (4) having security vulnerabilities. 
In this study, we focus on the first two forms of toxic code snippets, outdated code and license-violating code,
as these two problems are still underexplored compared to code smells~\cite{Tufano2015} and vulnerabilities~\cite{Acar2016,Fischer2017}.
Moreover, Stack Overflow users also express their concerns about these two problems
as shown in several discussion threads\footnote{Discussions about outdated answers and code license on
	Stack Overflow: meta.stackexchange.com/questions/131495, 
	meta.stackexchange.com/questions/11705/, meta.stackexchange.com/questions/12527,
	meta.stackexchange.com/questions/25956, meta.stackoverflow.com/questions/321291.}
	 on \textsf{meta.stackexchange.com} about outdated
answers and license of code on Stack Overflow.
Outdated code snippets can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license, e.g.,\ GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting licenses, legal issues may occur.

@@

We performed a detailed investigation of the 100 outdated answers on Stack
Overflow, on 6 May 2018, approximately two years after the snapshot we analysed was created
to look for any changes, warnings, or mitigations made to the outdated code snippets.
We investigated the answers on three aspects: newer answers, higher-voted answers, and comments on the
outdated answers. We found
34 posts which contained newer answers and 5 posts which contained answers with a higher number of
votes than the outdated answers. However, 99 of the 100 outdated answers were still
marked as accepted answers. For the comments, we check if there is any comment
to mitigate or point out the toxicity of the outdated code snippets. We found
that, out of 100 answers, 6 answers had a comment saying the
code in the answer is outdated or containing issues, such as \textit{``spring
	3.1 stuff''}, \textit{``...tried this but having connect exception --
	\texttt{javax.mail.MessagingException}:\textit{ Could not connect to SMTP host:
	\texttt{smtp.gmail.com}, port: 465''}, ``You should add a \texttt{buffer.reset(null, 0, 0);} at the end of the try block to avoid excess heap usage (issue no. HADOOP-11323)''} or \textit{``.. I do not have experience
	with new versions of hibernate for a long time. But previously without clean you
	could receive some unexpected results. So I suggest to try different approaches
	or even check latest documentation''}. The 6 outdated code snippets were still
not fixed, but the comments themselves may help to warn some of the Stack Overflow
users.

>>>>

Toxic code snippets mean code snippets that, after incorporating into software, degrades the software quality.
Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1)~outdated, (2)~violating their original software
license, (3) exhibiting code smells, or (4) having security vulnerabilities. 
In this study, we focus on the first two forms of toxic code snippets, outdated code and license-violating code,
as these two problems are still underexplored compared to code smells~\cite{Tufano2015} and vulnerabilities~\cite{Acar2016,Fischer2017}.
Moreover, Stack Overflow users also express their concerns about these two problems
as shown in several discussion threads\footnote{Discussions about outdated answers and code license on
	Stack Overflow: meta.stackexchange.com/questions/131495, 
	meta.stackexchange.com/questions/11705/, meta.stackexchange.com/questions/12527,
	meta.stackexchange.com/questions/25956, meta.stackoverflow.com/questions/321291.}
	 on \textsf{meta.stackexchange.com} about outdated
answers and license of code on Stack Overflow.
Outdated code snippets can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license, e.g.,\ GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting licenses, legal issues may occur.

@@

We performed a detailed investigation of the 100 outdated answers on Stack
Overflow, on 6 May 2018, approximately two years after the snapshot we analysed was created
to look for any changes, warnings, or mitigations made to the outdated code snippets.
We investigated the answers on three aspects: newer answers, higher-voted answers, and comments on the
outdated answers.\footnote{We also found that the Stack Overflow question ID 22262310 that has an outdated code answer from \texttt{WritableComparator.java} (\Cref{fig:before-after}), has a negative score of -1. It is interesting to see if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question. However, it is out of the scope of this study so we leave it as future work.} We found
34 posts which contained newer answers and 5 posts which contained answers with a higher number of
votes than the outdated answers. However, 99 of the 100 outdated answers were still
marked as accepted answers. For the comments, we check if there is any comment
to mitigate or point out the toxicity of the outdated code snippets. We found
that, out of 100 answers, 6 answers had a comment saying the
code in the answer is outdated or containing issues, such as \textit{``spring
	3.1 stuff''}, \textit{``...tried this but having connect exception --
	\texttt{javax.mail.MessagingException}:\textit{ Could not connect to SMTP host:
	\texttt{smtp.gmail.com}, port: 465''}, ``You should add a \texttt{buffer.reset(null, 0, 0);} at the end of the try block to avoid excess heap usage (issue no. HADOOP-11323)''} or \textit{``.. I do not have experience
	with new versions of hibernate for a long time. But previously without clean you
	could receive some unexpected results. So I suggest to try different approaches
	or even check latest documentation''}. The 6 outdated code snippets were still
not fixed, but the comments themselves may help to warn some of the Stack Overflow
users.

### 2018-11-15 cloverflow-tse/cover_letter/second_round/cover_letter.tex
Finalised the response letter. Ready for Jens to look at.

Thank you for your insightful comment regarding the toxic license violations. As the reviewer has mentioned, software license violation is difficult to identify and validate due to various number of software licenses, differences in country's legislation, and amount of code to be considered copyrighted (vs.~fair use). Nevertheless, the case of copying a licensed code snippet from an open source project to Stack Overflow without its license shows a clear potential for software license violation. By detecting such case, we can alleviate the license issues by stopping the accidental conversion of strictly licensed code (such as GPL) to permissively licensed code (such as CC BY-SA 3.0 on Stack Overflow). We hope that our study will raise awareness about this issue to Stack Overflow and the developers.

@@

We have moved the references for Black Duck Software and nextB to their first appearance on Page 17.

@@

@@

We agree that our analysis may not fully answer your comment because we could not capture what the Stack Overflow visitors actually did when they found an outdated answer. However, our investigation compared the popularity of the outdated answer and the newer answers based on the number of votes. If Stack Overflow visitors reuse the code (or learn from the answers) and they like the answer, they can reward the answer with an upvote. In our investigation of the 100 outdated answers, we found that only 5 of the newer answers had higher votes than the outdated answers and 99\% of the outdated answers were still marked as accepted. \FIXME{Shall we also discuss the issue of ``accepted answers'' that they are totally relied on the questioner and not other visitors?} We are aware that this may be affected by the duration that the answers appear on a Stack Overflow post. The newer answers have less visibility compared to the older answers.

An alternative solution might be directly comparing the number of code reuse from the outdated answers to their newer/higher-voted answers in open source projects (e.g., GitHub). 
Nevertheless, although we had performed such comparison, we would still suffer from the same timing issue that the newer code snippets have less chance to be reused than the older ones.

@@

The 100 posts are the posts containing the 100 outdated code snippets reported in RQ4. The 6 intents of changes in the 100 outdated code snippets shown in the table below (a copy of Table 3 in the previous response letter and Table 20 in the paper) cover \textbf{all} the cases of outdated code.

@@

The Deprecation intent partially indicates the cause of outdated code, but not all. It represents the code snippets that are outdated due to the use of deprecated functions or APIs. With this case of function/API deprecation, the code snippets that we analysed contained a few deprecated code statements while the newest version (based on the time we did the analysis) of the same code snippets no longer contain the deprecated part(s). Other intents represent different cases of a code snippet being outdated. For example, the Bug intent represents a code snippet that previously contained buggy code statements, and was fixed in the newest version. The Refactoring intent represents a code snippet that was different from the newest version due to code refactoring.
To sum up, the table shows that outdated code can be caused by different intents and not all of them are harmful. Outdated code snippets with Bug intent are clearly harmful if they are posted on the Internet (e.g., Stack Overflow). We slightly modified the section explaining this table to be clearer \FIXME{To do}.

@@

We understand your concern about the age of the data set. However, we do not expect large differences of the findings if we update the data set. The reason is that the Stack Overflow answers are rarely modified. As discussed in RQ4, we used this 2-year gap between the Stack Overflow snapshot that we analysed for clones, and the latest version on the web, as a chance to study the evolution of the 100 outdated answers. We found that 99\% of the outdated code are still marked as accepted. While there were a few newer posts in each of the 100 outdated answers, only 5 newer answers obtained higher votes than the outdated ones. Thus, updating the Stack Overflow data to the latest snapshot will mostly increase the chance of finding newer outdated code snippets.
We have added this to the Threats to Validity section \FIXME{To do}.

The 100 posts are the posts containing the 100 outdated code snippets reported in RQ4. Their analysis shows that only a number of the outdated code snippets are harmful. 47 of the 100 discovered outdated code are found in GitHub projects (12 are buggy code). So, according to the 111 Java projects in Qualitas, the outdated code snippets do not widely spread to open source projects.

@@

The verification was performed by the first and
the third authors. The two investigators separately went through each clone pair
candidate, looked at the clones, and decided if they are a true positive or a
false positive and classified them into an appropriate pattern. After the
validation, the results from the two investigators were compared. 
This discussion can be found in Section 2.2.3 (Manual investigation).

@@

``100 of them were found to be outdated\textbf{, of which 12 were buggy code.}'' \FIXME{update in the paper}

@@

@@

We have added a discussion of the point (c) in the ??? section. \FIXME{To do}

Reviewer 1 Comment 5:
``\textit{(c) if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question.}''

>>>>

We would like to thank you for your insightful comment regarding the toxic license violations. As the reviewer has mentioned, software license violation is difficult to identify and validate due to various number of software licenses, differences in country's legislation, and amount of code to be considered copyrighted (vs.~fair use). Nevertheless, the case of copying a licensed code snippet from an open source project to Stack Overflow without its license shows a clear potential for software license violation. By detecting such case, we can alleviate the license issues by stopping the accidental conversion of strictly licensed code (such as GPL) to permissively licensed code (such as CC BY-SA 3.0 on Stack Overflow). We hope that our study will raise awareness about this issue to Stack Overflow and the developers.

@@

Thank you for the comment. We have moved the references for Black Duck Software and nextB to their first appearance on Page 17.

@@

Thank you for the suggestion on the definition of toxic code snippets. Since Reviewer 3 also expresses his/her concern regarding the definition, we revised the definition by removing the technical debt part and shorting it as follows:

``Toxic code snippets mean code snippets that, after incorporating into software, degrades the software quality.
Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1)~outdated, (2)~violating their original software
license, (3) exhibiting code smells, or (4) having security vulnerabilities.''

We believe it is important to differentiate the definition of toxic code snippets from the concrete example of toxic code snippets on Stack Overflow since the idea of toxic code snippets can be applied to any other online sources (e.g., GitHub) as well.

@@

We agree that our analysis may not fully answer your comment because we could not capture what the Stack Overflow visitors actually did when they already expect an outdated answer. The most proper method for this may be doing another developer survey. However, our investigation tries to at least shade light on this by comparing the popularity of the outdated answer and the newer answers based on the number of votes. If Stack Overflow visitors reuse the code (or learn from the answers) and they like the answer, they can reward the answer with an upvote. In our investigation of the 100 outdated answers, we found that only 5 of the newer answers had higher votes than the outdated answers and 99\% of the outdated answers were still marked as accepted. \FIXME{Shall we also discuss the issue of ``accepted answers'' that they are totally relied on the questioner and not other visitors?} We are aware that this may be affected by the duration that the answers appear on a Stack Overflow post. The newer answers have less visibility compared to the older answers.

An alternative solution might be directly comparing the number of code reuse from the outdated answers to their newer/higher-voted answers in open source projects (e.g., GitHub). 
Nevertheless, although we had performed such comparison, we would still suffer from the same timing issue as the newer answers have shorter window to be reused than the older ones.

@@

The 100 posts are the posts containing the 100 outdated code snippets reported in RQ4. The 6 intents of changes in the 100 outdated code snippets, as shown in the table below (a copy of Table 3 in the previous response letter and Table 20 in the paper), cover \textbf{all} the cases of outdated code.

@@

The Deprecation intent partially indicates the cause of outdated code, but not all. It represents the code snippets that are outdated due to the use of deprecated functions or APIs. With this case of function/API deprecation, the code snippets that we analysed contained a few deprecated code statements while the newest version (based on the time we did the analysis) of the same code snippets no longer contain the deprecated part(s). The five other intents represent other cases of a code snippet being outdated. For example, the Bug intent represents a code snippet that previously contained buggy code statements, and was fixed in the newest version. The Refactoring intent represents a code snippet that was different from the newest version due to code refactoring.
To sum up, the table shows that outdated code can be caused by different intents and not all of them are harmful. Outdated code snippets with Bug intent are clearly harmful if they are posted on the Internet (e.g., Stack Overflow). We slightly modified the section explaining this table to be clearer \FIXME{To do}.

@@

We understand your concern about the age of the data set. However, we do not expect large differences of the findings if we update the data set. The reason is that the Stack Overflow answers are rarely modified. As discussed in RQ4, we used this 2-year gap between the Stack Overflow snapshot that we analysed for clones, and the latest version on the web, as a chance to study the evolution of the 100 outdated answers. We found that 99\% of the outdated code are still marked as accepted. While there were a few newer posts in each of the 100 outdated answers, only 5 newer answers obtained higher votes than the outdated ones. Thus, updating the Stack Overflow data to the latest snapshot will mostly increase the chance of finding newer outdated code snippets.
Nonetheless, we have added a discussion of the age of the Stack Overflow data set to the Threats to Validity section \FIXME{To do}.

The 100 posts are the posts containing the 100 outdated code snippets reported in RQ4. Their analysis shows the following. 
\begin{enumerate}
	\item Although they are outdated, after 2 years they still have higher votes than other answers or they are still marked as accepted answers.
	\item There is only 6\% of the outdated answers that have newer answers that mitigate or point out the toxicity of the outdated code snippets. 
	\item 47 of the 100 discovered outdated code are found in GitHub projects, of which 12 are buggy code. So, based on the 111 Java projects in Qualitas, their outdated code snippets do not widely spread to open source projects.
\end{enumerate}

@@

The investigation was performed by the first and
the third authors. The two investigators separately went through each clone pair
candidate, looked at the clones, and decided if they are a true positive or a
false positive and classified them into an appropriate pattern by following the steps show in Figure 5. 
After the validation, the results from the two investigators were compared. 
This discussion can be found in Section 2.2.3 (Manual investigation).

@@

``100 of them were found to be outdated\textbf{, of which 10 were buggy code.}'' \FIXME{update in the paper}

@@

After incorporating yours and Reviewer 2's comment, we revised the definition of toxic code snippets to be more concise and removed the focus on technical debt as follows.

``Toxic code snippets mean code snippets that, after incorporating into software, degrades the software quality.''

@@

We have added a discussion of the point (c) as a footnote in Section 4 as shown below.

``We also found that the Stack Overflow question ID 22262310 that has an outdated code answer from \texttt{WritableComparator.java} (Figure 1), has a negative score of -1. It is interesting to see if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question. However, it is out of the scope of this study so we leave it as future work.''
